JMLR-14-133-3: Point-to-Point Reply

### 2014-10-29 pkg/partykit/inst/mloss/review3/p2p.tex
typo
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@632 255f4249-2263-4417-b1ea-8498779e27a7

Of course, we can easily copy the code of the old \texttt{party::cforest} into the
new \emph{partykit} package. However, the usefulness for the practitioner would not
really be increased by this (given that \emph{party} is easily available). More
importantly, if we take the recommendations of Reviewer~2 seriously (which we do),
then we should not just copy existing code but build new extensible infrastructure
for forests as well. If we only copy the old code now, future developments are likely
to change at least parts of the interface and thus potentially breaking full
backward compatibility. Therefore, we would much rather follow Reviewer~2 and devote
more future work to this important topic.

>>>>

Of course, we can easily copy the code of the old \texttt{party::cforest} into the
new \emph{partykit} package. However, the usefulness for the practitioner would not
really be increased by this (given that \emph{party} is easily available). More
importantly, if we take the recommendations of Reviewer~2 seriously (which we do),
then we should not just copy existing code but build new extensible infrastructure
for forests as well. If we only copy the old code now, future developments are likely
to change at least parts of the interface and thus potentially break full
backward compatibility. Therefore, we would much rather follow Reviewer~2 and devote
more future work to this important topic.
